\documentclass{muratcan_cv}

\setname{Andrew}{Vagliano}
\setaddress{Washington, DC}
\setmobile{(860) 806-3910}
\setmail{andrew.vagliano1@gmail.com}
\setlinkedinaccount{andrew-vagliano}
\setgithubaccount{afv22}

\definecolor{themecolor}{HTML}{4E2A84}

\begin{document}
%
\headerview
\vspace{1ex}
%
\section{Summary}
\textblock{
    \smallskip
    Security software engineer with 3+ years of experience analyzing and mitigating highly
    sophisticated threats to global-scale networks. Seeking to leverage threat intelligence
    expertise and technical skills in cybersecurity roles. Skilled at designing user-centric
    security solutions and bridging technical and non-technical expertise.
    \smallskip
}

%
\section{Skills}
\newcommand{\skillone}{\createskill{Languages}{
        Python \cpshalf
        PHP / Hack \cpshalf
        Javascript / Typescript \cpshalf
        Haskell \cpshalf
        Rust \cpshalf
        SQL
    }}
%
\newcommand{\skilltwo}{\createskill{Technologies}{
        React \cpshalf
        GraphQL \cpshalf
        Dataswarm / Airflow \cpshalf
        AWS \cpshalf
        Cloudflare \cpshalf
        Docker \cpshalf
        Kali Linux
    }}
%
\newcommand{\skillthree}{\createskill{Areas of Expertise}{
        Data Engineering \cpshalf
        Threat Modeling \cpshalf
        AI Solutions \cpshalf
        Full-Stack Engineering \cpshalf
        Data Analysis
    }}
\newcommand{\skillfour}{\createskill{Personal Interests}{
        Motorsports \cpshalf
        Home Automation \& Self-Hosting \cpshalf
        Jazz \& Bluegrass Guitar \cpshalf
        College Football
    }}
%
\createskills{\skillone, \skilltwo, \skillthree, \skillfour}
\vspace{-3mm}
%
\section{Experience}
%
\datedexperience{Meta Platforms, Inc.}{Sep 2021 - Sep 2024}
\explanation{Security Engineer, Integrity Investigations \& Intelligence (i3)}{Washington, DC}
\explanationdetail{
    \smallskip
    \begin{itemize}
        %
        \item Led engineering efforts for trust \& safety intelligence teams; prototyped tools,
              standardized analyst workflows, and advocated for investigator needs to influence
              scaled solutions.
              %
        \item Architected end-to-end system to combat sex trafficking by translating expert knowledge
              into structured decision trees; built development and testing interface; implemented human
              review and escalation infrastructure; process and tooling were adopted by all high-priority
              problem spaces to monitor performance of scaled ML models.
              %
        \item Developed an AI system to modify severe content, reducing psychological impact on
              content moderators, improving retention and review speed; led cross-functional
              collaboration from UX research through launch.
              %
        \item Designed and executed testing procedure to identify community standards policy
              miscalibration and moderator bias; conducted statistical analysis to refine policy
              wording and improve precision, enabling global launch.
              %
        \item Triaged and resolved technical incidents and reputational escalations across
              an ecosystem of hundreds of legacy data pipelines, tools, and systems, balancing
              rapid fixes with long-term systemic solutions.
              %
        \item Mentored new hires through curated onboarding tasks and partner connections; conducted
              technical interviews to evaluate candidates.
              %
    \end{itemize}
    \smallskip
}
%
\datedexperience{Meta Platforms, Inc.}{Summer 2020}
\explanation{Security Engineer Intern, Threat Discovery}{Remote}
\explanationdetail{
    \smallskip
    \begin{itemize}
        %
        \item Adapted an account clustering system to surface and classify decentralized conspiracy
              networks, enabling one of the company's then-largest takedowns of a dangerous conspiracy
              movement.
              %
        \item Integrated OSINT sources and vendor data with internal tooling to improve off-platform
              investigative coverage.
              %
    \end{itemize}
    \smallskip
}
%
\datedexperience{American University}{Summer 2019}
\explanation{Summer Research Assistant}{Washington, DC}
\explanationdetail{
    \smallskip
    \begin{itemize}
        %
        \item Developed an ML pipeline for a model leveraging NLP techniques to predict and identify
              malicious sequences of system calls in continuous network traffic, addressing the
              challenge of unstructured and variable call patterns.
              %
    \end{itemize}
    \smallskip
}
%
\section{Notable Projects}
\smallskip
%
\datedexperience{Personal Zero-Trust Environment}{February 2025}
\explanationdetail{
    \medskip
    \begin{itemize}
        %
        \item Established a comprehensive zero-trust architecture using Cloudflare to enhance personal
              digital security.
              %
        \item Deployed DNS filtering and encrypted tunneling to reduce online tracking and prevent
              MITM attacks.
              %
        \item Configured secure remote access to services hosted on AWS and a private server,
              preventing unprivileged access.
    \end{itemize}
    \smallskip
}
%
\datedexperience{Venture Capital Matchmaker}{March 2025}
\explanationdetail{
    \smallskip
    \begin{itemize}
        %
        \item Developed an automated matching platform for a non-profit using Airtable and custom
              scripts to connect venture investors with relevant early-stage startups and generate
              personalized emails for each stakeholder.
        \item Eliminated manual matching, accelerating time-to-investment by improving discovery speed and match quality.
              %
    \end{itemize}
    \smallskip
}
%
\section{Education}
\smallskip
\datedexperience{Northwestern University, McCormick School of Engineering}{2017 - 2021}
\explanation{
    Computer Science, B.S. \cpshalf
    International Studies Minor \cpshalf
    Pi Kappa Alpha Fraternity
}{Evanston, IL}
%
\datedexperience{The Hotchkiss School}{2013 - 2017}
%
\section{Publications}
\smallskip
%
\datedexperience{
    Feature Extraction Based on Word Embedding Models for Intrusion Detection in Network Traffic
}{2020}
\explanation{Journal of Surveillance, Security, and Safety}{}
%
\end{document}
